Estimating duration in the presence of misclassification

### 2024-02-20 symbols.tex
proof ch 6

From chapter 5
\begin{itemize}
    \item $b_i$ the day infection episode $i$ begins
    \item $\set{D}$ the set of test schedules with a detected infection episode
    \item $d_i$ the duration of infection episode $i$
    \item $e_i$ the day infection episode $i$ ends
    \item $f_A(t)$ the pdf of the duration estimate from chapter 4
    \item $f_C(t)$ the pdf of the duration estimate from Walker's analysis
    \item $k_t$ the belief in the ATACCC estimate at time $t$
    \item $h_t$ the estimate of the hazard at time $t$ according to ATACCC
    \item $p_{ia}$ the probability of an admissible infection episode occurring in an individual with test schedule $\sched_i$
    \item $p_{i\bar{a}}$ the probability of an inadmissible infection episode occurring in an individual with test schedule $\sched_i$
    \item $p_{iu}$ the probability of an undetected infection episode occurring in an individual with test schedule $\sched_i$
    \item $\Ncis$ the number of individuals in CIS
    \item $\ndet$ the number of detected infection episodes
    \item $n_{ia}$ the number of admissible infection episodes in individuals with test schedule $\sched_i$
    \item $n_{i\bar{a}}$ the number of inadmissible infection episodes in individuals with test schedule $\sched_i$
    \item $n_{iu}$ the number of undetectable infection episodes in individuals with test schedule $\sched_i$
    \item $n_\sched$ the number of unique test schedules in CIS
    \item $\ntot$ the total number of infection episodes
    \item $\nnodet$ the number of undetected infection episodes
    \item $\alpha_0$ the prior in the absence of ATACCC data
    \item $\alpha_i$ the admissible space for test schedule $i$
    \item $\beta_0$ the prior in the absence of ATACCC data
    \item $\beta_i$ the inadmissible space for test schedule $i$
    \item $\epsilon_t$ the random part of the RW2 model for $\lambda_{t+1}$
    \item $\eta_i$ the number of individuals with test schedule $i$
    \item $\theta$ the survival function parameters
    \item $\lambda_t$ the hazard at time $t$
    \item $\mu_{\epsilon_1}$ the mean of the prior on $\epsilon_1$
    \item $\mu_{\lambda_1}$ the mean of the prior on $\lambda_1$
    \item $\mu_\sigma$ the mean of the prior on $\sigma$
    \item $\sigma$ the standard deviation of the RW2 prior on $\lambda_t$
    \item $\sigma_{\epsilon_1}$ the standard deviation of the prior on $\epsilon_1$
    \item $\sigma_{\lambda_1}$ the standard deviation of the prior on $\lambda_1$
    \item $\tau_{\sched_i}(t)$ the time between $t$ and the next test for test schedule $i$
    \item $\Omega_i^C$ the undetected space for test schedule $i$
\end{itemize}

>>>>

From chapter 5
\begin{itemize}
    \item $b_i$ the day infection episode $i$ begins
    \item $\set{D}$ the set of test schedules with a detected infection episode
    \item $d_i$ the duration of infection episode $i$
    \item $e_i$ the day infection episode $i$ ends
    \item $f_A(t)$ the pdf of the duration estimate from chapter 4
    \item $f_C(t)$ the pdf of the duration estimate from Walker's analysis
    \item $k_t$ the belief in the ATACCC estimate at time $t$
    \item $h_t$ the estimate of the hazard at time $t$ according to ATACCC
    \item $p_{ia}$ the probability of an admissible infection episode occurring in an individual with test schedule $\sched_i$
    \item $p_{i\bar{a}}$ the probability of an inadmissible infection episode occurring in an individual with test schedule $\sched_i$
    \item $p_{iu}$ the probability of an undetected infection episode occurring in an individual with test schedule $\sched_i$
    \item $\Ncis$ the number of individuals in CIS
    \item $\ndet$ the number of detected infection episodes
    \item $n_{ia}$ the number of admissible infection episodes in individuals with test schedule $\sched_i$
    \item $n_{i\bar{a}}$ the number of inadmissible infection episodes in individuals with test schedule $\sched_i$
    \item $n_{iu}$ the number of undetectable infection episodes in individuals with test schedule $\sched_i$
    \item $n_\sched$ the number of unique test schedules in CIS
    \item $\ntot$ the total number of infection episodes
    \item $\nnodet$ the number of undetected infection episodes
    \item $r$ the dispersion of the prior on $\ntot$
    \item $\sched_i$ the $i$th unique test schedule
    \item $\alpha_0$ the prior in the absence of ATACCC data
    \item $\alpha_i$ the admissible space for test schedule $i$
    \item $\beta_0$ the prior in the absence of ATACCC data
    \item $\beta_i$ the inadmissible space for test schedule $i$
    \item $\epsilon_t$ the random part of the RW2 model for $\lambda_{t+1}$
    \item $\eta_i$ the number of individuals with test schedule $i$
    \item $\theta$ the survival function parameters
    \item $\lambda_t$ the hazard at time $t$
    \item $\mu$ the mean of the prior on $\ntot$
    \item $\mu_{\epsilon_1}$ the mean of the prior on $\epsilon_1$
    \item $\mu_{\lambda_1}$ the mean of the prior on $\lambda_1$
    \item $\mu_\sigma$ the mean of the prior on $\sigma$
    \item $\sigma$ the standard deviation of the RW2 prior on $\lambda_t$
    \item $\sigma_{\epsilon_1}$ the standard deviation of the prior on $\epsilon_1$
    \item $\sigma_{\lambda_1}$ the standard deviation of the prior on $\lambda_1$
    \item $\tau_{\sched_i}(t)$ the time between $t$ and the next test for test schedule $i$
    \item $\Omega_i^C$ the undetected space for test schedule $i$
\end{itemize}

From chapter 6
\begin{itemize}
    \item $p_{ia}'$ the replacement for $p_{ia}$ including false negatives
    \item $p_{iu}'$ the replacement for $p_{iu}$ including false negatives
    \item $\psens$ test sensitivity
    \item $r\inform$ the dispersion of the informative prior on $\ntot$
    \item $y_i(t)$ the test result for infection episode $i$ at time $t$
    \item $\vec{y_i}$ the test results associated with infection episode $i$
    \item $\eta$ the additional probability of missing an infection episode due to false negatives
    \item $\mu\inform$ the mean of the informative prior on $\ntot$
    \item $\tau_{\sched_i}(t)$ the time between $t$ and the next but one test for test schedule $i$
\end{itemize}
